### 2021-07-06 ch/2-related-work.tex
Fix all minor issues

\subsection{Fair representations}\label{sec:fair-representation}
\citet{zemel2013learning} approach the problem of biased training data more directly
by seeking to transform the features, such that all traces of the sensitive attribute are removed,
while at the same time letting the features still carry the information required for predicting the class label.
% \citet{zemel2013learning} expand on the idea of creating a \emph{fair representation}.
% That is, the features of the data points are transformed such that all bias is removed
This is different from \citet{kamiran2009classifying} where the dataset was transformed as well,
but there, the change was to the \emph{labels}.
The idea of transforming the features assumes that the main problem with the data
are unwanted dependencies between $s$ and the other features (called \emph{latent prejudice} in \citet{kamishima2012fairness}),
and that the training labels are mostly unproblematic.
The intended result is then that classifiers trained on the transformed data will make $s$-invariant predictions `by default',
because they do not know about $s$.

@@

In this ``oblivious'' setting, the authors define their fairness criteria in terms of statistical independence:
\acf{EOdds} refers to the case where \(\hat{y}\) and \(s\) are independent conditional on \(y\).
This is equivalent to the true positive rate and the false positive rate being the same for all groups.
\ac{EOpp} is, as mentioned above,
the case where just the true positive rate is the same for all groups.
This means that \(\hat{y}\) and \(s\) are independent conditional on \(y=1\).
One of the main advantages of these definitions compared to \ac{DP} is that a perfect predictor satisfies them on any evaluation set.
% Demographic Parity is at odds with achieving perfect accuracy.
% Furthermore, for Demographic Parity a classifier might be forced to give a positive prediction to a lot of individuals
% where it is really not appropriate.

@@

In a follow-up work, \citet{zafar2017fairnesstreatment} adapt their work to avoid ``disparate mistreatment''.
Avoiding disparate mistreatment is the same as enforcing \acf{EOdds},
as defined in the contemporary work by \citet{hardt2016equality}.
As in the previous work, they define a tractable proxy for this measure.
To this end, they first define a function \(g\) that measures
how well the class label \(y \in \{0, 1\}\) and the predicted score for a data point \(0 \leq f(x) \leq 1\) agree:
\begin{align}
  \label{eq:zafar-constraint-2}
  g(y, x) = \min \left(0, \left(y - \tfrac{1}{2}\right) \cdot \left(f(x) - \tfrac{1}{2}\right)\right)
\end{align}
Subtracting \(\tfrac{1}{2}\) is necessary to centre the values around \(0\).
The proxy for \ac{EOdds} is then the covariance between the sensitive attribute and \(g\).
\(g\) can also be modified to only take into account cases with \(y=1\) which corresponds to enforcing \acf{EOpp.
The paper contains experiments on the ProPublica/COMPAS dataset~\citep{angwin2016machine}.
The task for this dataset is to predict
whether a criminal offender committed another misconduct or felony within two years,
based on personal information that includes age, gender, race and past criminal history.
% The authors compare the proposed method to an implementation of the algorithm from \citet{hardt2016equality}.
% In the Equality of Opportunity task, the approach by \citet{hardt2016equality} performs better
% (lower discrimination, similar accuracy).
% The better performance is likely at least partially explained
% by \citet{hardt2016equality} using the sensitive attribute for predictions.
% The evaluation metric is
% the difference in FPR (false positive rate) and the difference in FNR (false negative rate) between the two groups.
% Hardt et al.~achieve an FPR difference of 0.02 at 66\% accuracy while Zafar et al.~achieve an FPR difference of
% 0.06 at the same 66\% accuracy.
% For Equalised Odds,
% the proposed approach achieves higher accuracy but also higher discrimination than in \citet{hardt2016equality}.
% One limiting factor that the authors identify is the size of the dataset:
% the degree of discrimination cannot be accurately estimated by the algorithm if the dataset is small.

@@

A contemporary paper by \citet{kusner2017counterfactual} approaches the problem differently.
In this paper, a new fairness criterion which they call ``counterfactual fairness''
is defined making use of causal reasoning.
For the definition, they assume access to a causal model
that can be used to compute \emph{counterfactuals} (for example a structural equation model \citep{kaplan2008structural}).
This is in contrast to \citet{kilbertus2017avoiding} who relied on just \emph{interventions}.
(According to Pearl's causal hierarchy \citep{pearl2019seven},
counterfactuals require a deeper level of causal information than interventions.)
The causal model depends on unobserved background variables \(U\),
non-sensitive features \(x\) and a sensitive attribute \(s\).
A predictor \(\hat{y}\) is then \emph{counterfactually fair}
if the following equality of \emph{counterfactual probabilities} holds:
\begin{align}
  \label{eq:counterfactual-fairness}
  P(\hat{y}_{s=i}(U) = 1|x, s=i)=P(\hat{y}_{s=j}(U) = 1|x, s=i)
\end{align}
where \(i, j \in \{0, 1\}\) and \(i \neq j\).
The first counterfactual probability is actually not a real counterfactual:
it is just the probability of observing \(\hat{y} = 1\)
given the background variables \(U\), the features \(x\) and \(s=i\).
The second counterfactual probability is the probability of observing \(\hat{y} = 1\)
given \(U\) and \(x\) and given that we had \(s=j\) instead of the actual value \(s=i\).
In other words, the criterion demands this:
the prediction would have been the same in the counterfactual world
where the sensitive attribute is \(j\) instead of \(i\).
In the counterfactual world, everything that is not causally dependent on \(s\) is held constant.

>>>>

\subsection{Fair representations}\label{sec:fair-representation}
\citet{zemel2013learning} approach the problem of biased training data more directly
by seeking to transform the features, such that all traces of the sensitive attribute are removed,
while at the same time letting the features still carry the information required for predicting the class label.
% \citet{zemel2013learning} expand on the idea of creating a \emph{fair representation}.
% That is, the features of the data points are transformed such that all bias is removed
This is different from \citet{kamiran2009classifying} where the dataset was transformed as well,
but there, the change was to the \emph{labels}.
The idea of transforming the features assumes that the main problem with the data
are unwanted dependencies between $s$ and the other features \citep[called \emph{latent prejudice} in ][]{kamishima2012fairness},
and that the training labels are mostly unproblematic.
The intended result is then that classifiers trained on the transformed data will make $s$-invariant predictions `by default',
because they do not know about $s$.

@@

In this ``oblivious'' setting, the authors define their fairness criteria in terms of statistical independence:
\acf{EOdds} refers to the case where \(\hat{y}\) and \(s\) are independent conditional on \(y\).
This is equivalent to the true positive rate and the false positive rate being the same for all groups.
\Acf{EOpp} is, as mentioned above,
the case where just the true positive rate is the same for all groups.
This means that \(\hat{y}\) and \(s\) are independent conditional on \(y=1\).
One of the main advantages of these definitions compared to \ac{DP} is that a perfect predictor satisfies them on any evaluation set.
% Demographic Parity is at odds with achieving perfect accuracy.
% Furthermore, for Demographic Parity a classifier might be forced to give a positive prediction to a lot of individuals
% where it is really not appropriate.

@@

In a follow-up work, \citet{zafar2017fairnesstreatment} adapt their work to avoid ``disparate mistreatment''.
Avoiding disparate mistreatment is the same as enforcing \acf{EOdds},
as defined in the contemporary work by \citet{hardt2016equality}.
As in the previous work, they define a tractable proxy for this measure.
To this end, they first define a function \(g\) that measures
how well the class label \(y \in \{0, 1\}\) and the predicted score for a data point \(0 \leq f(x) \leq 1\) agree:
\begin{align}
  \label{eq:zafar-constraint-2}
  g(y, x) = \min \left(0, \left(y - \tfrac{1}{2}\right) \cdot \left(f(x) - \tfrac{1}{2}\right)\right)
\end{align}
Subtracting \(\tfrac{1}{2}\) is necessary to centre the values around \(0\).
The proxy for \ac{EOdds} is then the covariance between the sensitive attribute and \(g\).
\(g\) can also be modified to only take into account cases with \(y=1\) which corresponds to enforcing \acf{EOpp}.
The paper contains experiments on the ProPublica/COMPAS dataset~\citep{angwin2016machine}.
The task for this dataset is to predict
whether a criminal offender committed another misconduct or felony within two years,
based on personal information that includes age, gender, race and past criminal history.
% The authors compare the proposed method to an implementation of the algorithm from \citet{hardt2016equality}.
% In the Equality of Opportunity task, the approach by \citet{hardt2016equality} performs better
% (lower discrimination, similar accuracy).
% The better performance is likely at least partially explained
% by \citet{hardt2016equality} using the sensitive attribute for predictions.
% The evaluation metric is
% the difference in FPR (false positive rate) and the difference in FNR (false negative rate) between the two groups.
% Hardt et al.~achieve an FPR difference of 0.02 at 66\% accuracy while Zafar et al.~achieve an FPR difference of
% 0.06 at the same 66\% accuracy.
% For Equalised Odds,
% the proposed approach achieves higher accuracy but also higher discrimination than in \citet{hardt2016equality}.
% One limiting factor that the authors identify is the size of the dataset:
% the degree of discrimination cannot be accurately estimated by the algorithm if the dataset is small.

@@

A contemporary paper by \citet{kusner2017counterfactual} approaches the problem differently.
In this paper, a new fairness criterion which they call ``counterfactual fairness''
is defined making use of causal reasoning.
For the definition, they assume access to a causal model
that can be used to compute \emph{counterfactuals} \citep[for example a structural equation model;][]{kaplan2008structural}.
This is in contrast to \citet{kilbertus2017avoiding} who relied on just \emph{interventions}.
(According to Pearl's causal hierarchy \citep{pearl2019seven},
counterfactuals require a deeper level of causal information than interventions.)
The causal model depends on unobserved background variables \(U\),
non-sensitive features \(x\) and a sensitive attribute \(s\).
A predictor \(\hat{y}\) is then \emph{counterfactually fair}
if the following equality of \emph{counterfactual probabilities} holds:
\begin{align}
  \label{eq:counterfactual-fairness}
  P(\hat{y}_{s=i}(U) = 1|x, s=i)=P(\hat{y}_{s=j}(U) = 1|x, s=i)
\end{align}
where \(i, j \in \{0, 1\}\) and \(i \neq j\).
The first counterfactual probability is actually not a real counterfactual:
it is just the probability of observing \(\hat{y} = 1\)
given the background variables \(U\), the features \(x\) and \(s=i\).
The second counterfactual probability is the probability of observing \(\hat{y} = 1\)
given \(U\) and \(x\) and given that we had \(s=j\) instead of the actual value \(s=i\).
In other words, the criterion demands this:
the prediction would have been the same in the counterfactual world
where the sensitive attribute is \(j\) instead of \(i\).
In the counterfactual world, everything that is not causally dependent on \(s\) is held constant.

### 2021-07-06 ch/4-structure.tex
Fix all minor issues

In order to construct the target labels,
we use side information about summary statistics for a balanced training set.
This allows us to target a specific balanced set, instead of just any balanced set.
In other words, rather than just enforcing \ac{DP}, the method gives control over the target rates \(P(\hat{y}=1|s)\).
These target rates are the only parameters of the model.
The target labels represent an uncertain estimate of labels corresponding to a balanced dataset.
Via the sum rule of probabilities, it is possible to express the model likelihood in terms of these target labels,
such that maximising the likelihood corresponds to improving the prediction of the target labels
instead of the given (biased) training labels.

@@

As an example, consider the scenario where someone wants to create a classifier
to distinguish between sheep and cows, that is supposed to work anywhere on earth.
However, they take a shortcut while creating the dataset
and take all their sheep images from hot and dry countries
and all their cow images from mild and rainy countries.
In this case, the dataset is lacking cow images in dry landscapes,
and is lacking sheep from green landscapes;
the dataset exhibits a strong sampling bias.
The result is that even though the labels correctly correspond to cows and sheep,
they do not point reliably to the right target anymore.
As background colour is easier to recognise with a \ac{CNN} than animal species,
the labels have effectively been turned into landscape labels.
In other words, landscape has become a \emph{spurious attribute}.
%
% As an example, consider a dataset where the task is to distinguish smiling from non-smiling faces.
% Say, we initially have a very diverse and balanced training set,
% but then, from the set of smiling faces, we remove nearly all samples where the person does not have red hair,
% and from the set of non-smiling faces, we remove nearly all samples with non-black hair.
% The result is that even though the labels are still correct, they do not point reliably to the right target anymore.
% As hair colour is easier to recognise with a \ac{CNN}, the labels have effectively been turned into hair colour labels.
% In other words, hair colour has become a \emph{spurious attribute}.
In the following, we denote the spurious attribute with \(s\),
as it takes a role that is very similar to that of the sensitive attribute that was also denoted by \(s\).
However, there is a difference in emphasis between a \emph{sensitive} and a \emph{spurious} attribute:
the former indicates that the attribute should not be used for legal or ethical reasons,
whereas the latter can be any attribute that is associated with the class label \(y\) in an undesired way
that leads to lower quality predictions.

The method, proposed in the previous paper (\chapref{ch:paper1}),
is not able to deal with such a dataset bias as we can easily see:
Say, \emph{smiling} corresponds to \(y=1\) and \emph{not smiling} to \(y=0\);
furthermore, let red hair correspond to \(s=1\), black hair to \(s=0\), and all other hair colours to \(s=2\).
Then, the problem with the described dataset is, that it mostly consists of samples with \(y=0\wedge s=0\)
and those with \(y=1\wedge s=1\).
If we call \(P(y=1|s=s')\) the acceptance rate,
then the problem can be described as one of very different acceptance rates in the hair colour groups given by \(s\).
This is the problem tackled in the previous paper,
and yet, if we were to equalise the acceptance rates with the method there,
the result would be very incorrect.
The issue is that we would treat the labels as incorrect, when in truth, they are correct.

To deal with sampling bias, a different approach is needed.
Indeed, the problem, as posed, is not solvable in the general case.
To make headway with this problem, we introduce the concept of a \emph{representative set}.
This set is not subject to the sampling bias,
but is unlabelled (with respect to $y$) and so does not by itself suffice for training.
However, this set does have labels for the spurious attribute \(s\).
This allows us to learn an \emph{invariant representation},
\ie, a representation of the input features \(x\) which is invariant to the spurious attribute.
This kind of representation is equivalent to a fair representation -- as described in \secref{sec:fair-representation} --
which is invariant to a sensitive attribute.
With the invariant representation of the training set,
a classifier can then be trained to accurately predict the class label \(y\).
The invariant representation cannot be learned from the training set
because there, due to the sampling bias, \(s\) and \(y\) are not distinguishable.

@@

The method presented in \citet{kehrenberg2020nullsampling} (\chapref{ch:paper2}) is based on the idea of \emph{null-sampling},
which refers to zeroing out part of an encoding,
and then reconstructing the modified encoding as if it were a normal encoding.
Before we apply null-sampling, an encoding of the input \(x\) is learned that is split into two parts:
\(z_u\), which has no information about the spurious attribute \(s\),
and \(z_b\), which has all information needed to reconstruct \(x\) that is not contained in \(z_u\).
\(z_u\) is ensured to be not predictive of \(s\) via adversarial training.
During null-sampling, \(z_b\) is zeroed out, and after decoding it,
we obtain an invariant representation \emph{in the data domain}.
The fact that it is in the data domain makes it interpretable.

@@

\section{Overcoming sampling bias with unlabelled deployment set}\label{sec:zsf}
A shortcoming of the approach from the previous publication \citep{kehrenberg2020nullsampling}
is its reliance on a representative set which has labels for the spurious attribute \(s\).
As discussed, it is necessary to make use of \emph{some} kind of side information,
but perhaps we can relax some requirements.
In particular, while it is already easier to collect data without \(y\) labels (but with \(s\) labels),
it is even easier to collect data without \emph{any} label.
Thus, requiring only an unlabelled context set would improve the applicability of the method.
\citet{kehrenberg2020zeroshot} (\chapref{ch:paper3}) presents an approach based on that idea.

The setting is very similar to the previous publication \citep{kehrenberg2020nullsampling}:
the training set suffers from severe sampling bias, but we have access to a (mostly) unbiased \emph{deployment set}
(similar to but not quite identical with the previously discusses \emph{representative set}).
The idea is that the deployment set corresponds to the setting in which the model is meant to be deployed.
The change is that this additional set may be completely unlabelled,
but in exchange, we have some stronger requirements for the training set.
Namely, the holes left by the sampling bias may not be so numerous
as to make \(s\) and \(y\) completely indistinguishable.
In the previous paper, the example of Coloured MNIST had a training set
where there was a strict one-to-one mapping of colour and digit;
but this kind of blending of \(s\) and \(y\) into one is not the focus of this paper.
The focus is instead on a setting where the training set lacks certain combinations of \(s\) and \(y\),
which results in poor predictions for these combinations on the test set (or deployment setting)
where those combinations \emph{do} occur.
We refer to these missing combinations as \emph{subgroup bias} or \emph{missing subgroups},
depending on whether a given \(s\) value appears in the training set at all.
The label \(s\) plays here a similar role to the spurious attribute in the previous publication,
but as there is a change in emphasis, we refer to \(s\) as \emph{subgroup label}%
\footnote{This terminology is inspired by the \emph{subclass} concept in \citet{SohDunAngGuetal20}.}
instead.
The difference between a spurious attribute and a subgroup label is that
the former is mostly characterised via its confusion with the prediction target,
whereas the latter refers to natural groups in the data
which have differing levels of annotation quality which affects the classification performance on these subgroups.
However, in both cases, the goal is to make the model output invariant to the \(s\) label.

As in the previous paper, the first step is to train a neural network to produce an invariant representation.
The second step is then to train a classifier on that.
The invariant representation is trained by performing distribution matching between the training set and the deployment set.
Finally, the training set is transformed into the invariant representation,
to serve as training set for the classifier.

The distribution matching is realised with adversarial networks which compare batches of samples,
in order to try to distinguish data drawn from the training set and the deployment set.
This process requires balanced batches as an inductive bias,
because the network will only learn the intended difference between training and deployment set,
if the drawn batches exhibit this difference.
For example, if batches drawn from Coloured MNIST differ not in colour but in digit class,
then distribution matching will learn to change digit shapes.
Balancing batches from the training set is easily possible with the available labels,
but those are not available for the deployment set,
so we use clustering techniques to identify the different groups in the deployment set,
and then draw samples for the batches at equal rate from all clusters.
It is important to note here that imperfections in the clustering are not a problem
as long as the show on average the intended difference between training and deployment set.

>>>>

In order to construct the target labels,
we use side information about summary statistics for a balanced training set.
This allows us to target a specific balanced set, instead of just any balanced set.
In other words, rather than just enforcing \ac{DP}, the method gives control over the target rates \(P(\hat{y}=1|s)\),
which are the only fairness-hyperparameters of the model.
The target labels \(\bar{y}\) represent an uncertain estimate of labels corresponding to a balanced dataset
(one where \(\bar{y} \perp s\)).
The idea is then the learn a predictor for these target labels instead of the given (biased) training labels \(y\).
Via the sum rule of probabilities, it is possible to express the model likelihood in terms of the target labels,
such that maximising the likelihood corresponds to improving the prediction of the target labels.

@@

As an example, consider the scenario where someone wants to create a classifier
to distinguish between sheep and cows, that is supposed to work anywhere on earth.
However, they take a shortcut while creating the dataset
and take all their sheep images from hot and dry countries
and all their cow images from mild and rainy countries.
In this case, the dataset is lacking cow images in dry landscapes,
and is lacking sheep from green landscapes;
the dataset exhibits a strong sampling bias.
The result is that even though the labels correctly correspond to cows and sheep,
they do not point reliably to the right target anymore.
As background colour is easier to recognise with a \ac{CNN} than animal species,
the labels have effectively been turned into landscape labels.
In other words, landscape has become a \emph{spurious attribute}.
%
% As an example, consider a dataset where the task is to distinguish smiling from non-smiling faces.
% Say, we initially have a very diverse and balanced training set,
% but then, from the set of smiling faces, we remove nearly all samples where the person does not have red hair,
% and from the set of non-smiling faces, we remove nearly all samples with non-black hair.
% The result is that even though the labels are still correct, they do not point reliably to the right target anymore.
% As hair colour is easier to recognise with a \ac{CNN}, the labels have effectively been turned into hair colour labels.
% In other words, hair colour has become a \emph{spurious attribute}.
In the following, we denote the spurious attribute with \(s\),
as it takes on a role that is very similar to that of the sensitive attribute that was also denoted by \(s\).
However, there is a difference in emphasis between a \emph{sensitive} and a \emph{spurious} attribute:
the former indicates that the attribute should not be used for legal or ethical reasons,
whereas the latter can be any attribute that is associated with the class label \(y\) in an undesired way
that leads to lower quality generalisation.

The method, proposed in the previous paper (\chapref{ch:paper1}),
is not able to deal with such a dataset bias as we can easily see:
Say, \emph{smiling} corresponds to \(y=1\) and \emph{not smiling} to \(y=0\);
furthermore, let red hair correspond to \(s=1\), black hair to \(s=0\), and all other hair colours to \(s=2\).
Then, the problem with the described dataset is, that it mostly consists of samples with \(y=0\wedge s=0\)
and those with \(y=1\wedge s=1\).
If we call \(P(y=1|s=s')\) the acceptance rate,
then the problem can be described as one of very different acceptance rates in the hair colour groups given by \(s\).
This is the problem tackled in the previous paper,
and yet, if we were to equalise the acceptance rates with the method there,
the result would be very incorrect.
The issue is that we would treat the labels as incorrect, when in truth, they are correct;
the problem with the data being sampling bias.

To deal with sampling bias, a different approach is needed.
Indeed, the problem, as posed, is not solvable in the general case.
To make headway with this problem, we introduce the concept of a \emph{representative set}.
This set is not subject to the sampling bias,
but is unlabelled (with respect to $y$) and so does not by itself suffice for training.
However, this set does have labels for the spurious attribute \(s\).
This allows us to learn an \emph{invariant representation},
\ie, a representation of the input features \(x\) which is invariant to the spurious attribute.
This kind of representation is equivalent to a fair representation -- as described in \secref{sec:fair-representation} --
which is invariant to a sensitive attribute.
With the invariant representation of the training set,
a classifier can then be trained to accurately predict the class label \(y\).
The invariant representation cannot be learned from the training set
because there, due to the sampling bias, \(s\) and \(y\) are not sufficiently distinguishable.

@@

The method implementing this general strategy, and presented in \citet{kehrenberg2020nullsampling} (\chapref{ch:paper2}),
is based on the idea of \emph{null-sampling},
which refers to zeroing out part of an encoding,
and then reconstructing the modified encoding as if it were a normal encoding.
In order to apply null-sampling, an encoding of the input \(x\) is learned that is split into two parts:
\(z_u\), which has no information about the spurious attribute \(s\),
and \(z_b\), which has all the remaining information needed to reconstruct \(x\) that is not contained in \(z_u\).
\(z_u\) is ensured to be not predictive of \(s\) via adversarial training.
During null-sampling, \(z_b\) is zeroed out, and after decoding it,
we obtain an invariant representation \emph{in the data domain}.
The fact that it is in the data domain makes it interpretable or inspectable.

@@

\section{Overcoming sampling bias with an unlabelled deployment set}\label{sec:zsf}
A shortcoming of the approach from the previous publication \citep{kehrenberg2020nullsampling}
is its reliance on a representative set which has labels for the spurious attribute \(s\).
As discussed, it is necessary to make use of \emph{some} kind of side information,
but perhaps we can relax some requirements.
In particular, while it is already easier to collect data without \(y\) labels (but with \(s\) labels),
it is even easier to collect data without \emph{any} label.
Thus, requiring only an unlabelled context set would improve the applicability of the method.
\citet{kehrenberg2020zeroshot} (\chapref{ch:paper3}) presents an approach based on that idea.

The setting is very similar to the previous publication \citep{kehrenberg2020nullsampling}:
the training set suffers from severe sampling bias, but we have access to a (mostly) unbiased \emph{deployment set}
(similar to but not quite identical to the previously discussed \emph{representative set}).
The idea is that the deployment set corresponds to the setting in which the model is meant to be deployed.
The change from the previous setting is that this additional set may be completely unlabelled,
but in exchange, we have some stronger requirements for the training set:
The holes left by the sampling bias may not be so numerous
as to make \(s\) and \(y\) completely indistinguishable.
For example, in the previous work, the example of Coloured MNIST had a training set
where there was a strict one-to-one mapping of colour and digit;
but this kind of blending of \(s\) and \(y\) into one is not the focus of this paper.
Instead, the focus is on a setting where the training set lacks certain combinations of \(s\) and \(y\),
which results in poor predictions for these combinations on the test set (or deployment setting)
where those combinations \emph{do} occur.
We refer to these missing combinations as \emph{subgroup bias} or \emph{missing subgroups},
depending on whether a given \(s\) value appears in the training set at all.
The label \(s\) plays here a similar role to the spurious attribute in the previous publication,
but as there is a change in emphasis, we refer to \(s\) as \emph{subgroup label}%
\footnote{This terminology is inspired by the \emph{subclass} concept in \citet{SohDunAngGuetal20}.}
instead.
The difference between a spurious attribute and a subgroup label is that
the former is mostly characterised via its confusion with the prediction target,
whereas the latter refers to natural groups in the data
which have differing levels of annotation quality which affects the classification performance on these subgroups.
However, in both cases, the goal is to make the model output invariant to the \(s\) label,
\ie the classification performance should be independent of the subgroup.

As in the previous paper, the first step is to train a neural network to produce an invariant representation.
The second step is then to train a classifier on said representation.
The invariant representation is trained by performing \emph{distribution matching} between the training set and the deployment set.
% Finally, the training set is transformed into the invariant representation,
% to serve as training set for the classifier.

The distribution matching is realised with adversarial networks which compare batches of samples,
in order to try to distinguish data drawn from the training set and the deployment set.
This process requires balanced batches as an inductive bias,
because the network will only learn the intended difference between training and deployment set,
if the drawn batches exhibit this difference.
For example, if batches drawn from Coloured MNIST differ not in colour but in digit class,
then distribution matching will learn to change digit shapes.
Balancing batches from the training set is easily possible with the available labels,
but those are not available for the deployment set,
so we use clustering techniques to identify the different groups in the deployment set,
and then draw samples for the batches at an equal rate from all clusters.
It is important to note here that imperfections in the clustering are not a problem
as long as the batches show on average the intended difference between training and deployment set.

### 2021-07-06 ch/6-discussion.tex
Fix all minor issues

There are also certain technical improvements that could be made.
In general, it would be desirable to have more theoretical bounds on performance.
This likely involves specifying the requirements for the algorithms more precisely.
% which is also useful information for potential users.
The method based on target labels would furthermore benefit from better-calibrated probability outputs.
\acf{GP} classifiers show generally good calibration,
but cannot be easily applied in domains where deep neural networks are used.
On the other hand, neural networks are known to be overconfident
(especially when using ReLU activations \citep{hein2019relu}),
so to apply the proposed method to images directly is not straightforward.
The other two proposed methods would benefit from improved adversarial training procedures.
Training these models is not straightforward as the losses have to be balanced
and in some cases, the update schedule needs to be changed.
Both the calibration of neural networks and the stability of adversarial training
are issues that are widely recognised in the \ac{ML} community,
so there is hope that progress will be made on these.

>>>>

There are also certain technical improvements that could be made.
In general, it would be desirable to have more theoretical bounds on performance.
This likely involves specifying the requirements for the algorithms more precisely.
% which is also useful information for potential users.
The method based on target labels would furthermore benefit from better-calibrated probability outputs.
\acf{GP} classifiers show generally good calibration,
but cannot be easily applied in domains where deep neural networks are used.
On the other hand, neural networks are known to be overconfident
\citep[especially when using ReLU activations;][]{hein2019relu},
so to apply the proposed method to images directly is not straightforward.
The other two proposed methods would benefit from improved adversarial training procedures.
Training these models is not straightforward as the losses have to be balanced
and in some cases, the update schedule needs to be changed.
Both the calibration of neural networks and the stability of adversarial training
are issues that are widely recognised in the \ac{ML} community,
so there is hope that progress will be made on these.
